---
title: |
  |   
  | Main Analyses: Early life adversity is associated with greater similarity in neural representations of ambiguous and threatening stimuli.

author: "Natalie Saragosa-Harris"
date: "October 2023"
output:
  html_document:
    toc: true
    toc_depth: 4
---

```{r settings, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read_data, include=FALSE}
library(plyr)
library(readr)
library(psych)
library(dplyr)
library(tidyr)
library(glue)
library(ggplot2)
library(lme4)
library(lmerTest)
library(sjPlot) #https://cran.r-project.org/web/packages/sjPlot/vignettes/tab_model_estimates.html
library(sjmisc)
library(sjlabelled)
library(stargazer) #https://zief0002.github.io/book-8252/pretty-printing-tables-in-markdown.html
library(reshape2)
library(vtable) # for summary tables (descriptive statistics).
library(gtsummary) # also for summary tables.
library(pander) # For formatting tables for t tests results.
library(patchwork)
library(ggeffects)
library(reghelper) # for simple slopes.
library(qwraps2)
options(qwraps2_markup = "markdown")
options(scipen=1, digits=2)

data <- read.csv('data/behavior_rsa_shortdata.csv',stringsAsFactors = TRUE) # Read in data.
long_behavioral_data <- read.csv('data/behavioraltask_longdata.csv',stringsAsFactors = TRUE)

# Behavioral trial level data: Edit response so that a positive rating = 0 and a negative rating = 1.
long_behavioral_data <- long_behavioral_data %>%
  mutate(response = case_when(P_N_response =="P" ~ 0,
                              P_N_response =="N" ~ 1))
# Only keep trials in which there is a response.
long_behavioral_data <- long_behavioral_data[complete.cases(long_behavioral_data$response),]
surprised_trials <- subset(long_behavioral_data, TrialType == "surprised")

```

```{r plot_themes, include=FALSE}
# Theme for plots.
nsh_theme <- theme(text = element_text(family = "Avenir"),
                   title = element_text(size=14, vjust=2, face="bold"),
                   plot.subtitle = element_text(size=14,color="gray40", face="bold.italic"),
                   axis.title.x= element_text(size=14, vjust=-0.3),
                   axis.title.y= element_text(size=14, vjust=1.5),
                   axis.text.x= element_text(size=14, colour="black"),
                   axis.text.y= element_text(size=14, colour="black"),
                   strip.text = element_text(size=14, face="bold"),
                   panel.background = element_blank(),
                   axis.line = element_line(colour = "black"))

# Color dictionary for plots, so that color matching is consistent.
fivecolors <- c("accumbens" = "#78B7C5",
                "amygdala" = "#EBCC2A",
                "anteriorinsula" = "#C5776C",
                "vmpfc" = "#9CB7B5",
                "V1" = "#A09CB0")
```

\newpage
<br>
<br>

## Accuracy for non-ambiguous (threatening and nonthreatening) images in post-scan task.
```{r postscan_task_accuracy,include=FALSE}
# One-tailed t-test to make sure accuracy is greater than 50% (chance accuracy).
percent_angry_correct <- t.test(data$Percent_Angry_Correct, mu = 0.50, alternative = "greater") # mean accuracy = 0.93; t(40) = 31; p < 0.001.
percent_happy_correct <- t.test(data$Percent_Happy_Correct, mu = 0.50, alternative = "greater") # mean accuracy = 0.96; t(40) = 72; p < 0.001.

```
 
```{r postscan_task_accuracy_table,echo=FALSE, warning=FALSE}
pander(percent_angry_correct, caption = "One-tailed t-test: Is average accuracy for threatening (angry) images greater than 50% (chance accuracy)?")
pander(percent_happy_correct, caption = "One-tailed t-test: Is average accuracy for nonthreatening (happy) images greater than 50% (chance accuracy)?")
```

## Reaction time by image type in post-scan task.
```{r angry_happy_reactiontime,echo=FALSE, warning = FALSE}

reactiontime_average_data <- data %>% select(Participant_ID, angry_rt_average, happy_rt_average,surprised_rt_average) %>%
  pivot_longer(!Participant_ID, names_to = "trial_type", values_to = "reactiontime_average")

reactiontime_sd_data <- data %>% select(Participant_ID, angry_rt_sd, happy_rt_sd, surprised_rt_sd) %>%
  pivot_longer(!Participant_ID, names_to = "trial_type", values_to = "reactiontime_sd")

reactiontime_average_data$trial_type <- gsub( "_rt_average", "",reactiontime_average_data$trial_type)
reactiontime_average_data$trial_type <- as.factor(reactiontime_average_data$trial_type)
reactiontime_sd_data$trial_type <- gsub("_rt_sd", "",reactiontime_sd_data$trial_type)
reactiontime_sd_data$trial_type <- as.factor(reactiontime_sd_data$trial_type)

reactiontime_data <- merge(reactiontime_average_data,reactiontime_sd_data,by=c("Participant_ID","trial_type"))

# Make surprised the reference level,so that angry and happy are being compared to surprised (as this is where we expect to see the difference).
reactiontime_by_trialtype <- lm(reactiontime_average ~ relevel(trial_type, ref = "surprised"), data = reactiontime_data)
#summary(reactiontime_by_trialtype)
#anova(reactiontime_by_trialtype)

# Paired t test between conditions.
surprised_angry_reactiontime <- t.test(data$surprised_rt_average, data$angry_rt_average, paired = TRUE, alternative = "two.sided")
surprised_happy_reactiontime <- t.test(data$surprised_rt_average, data$happy_rt_average, paired = TRUE, alternative = "two.sided")

```

```{r angry_happy_reactiontime_table,echo=FALSE, warning = FALSE}

pander(surprised_angry_reactiontime, caption = "Two-tailed t-test: Does average reaction time differ for ambiguous (surprised) images and threatening (angry) images?")
pander(surprised_happy_reactiontime, caption = "Two-tailed t-test: Does average reaction time differ for ambiguous (surprised) images and nonthreatening (happy) images?")

```

## Do trial-level reaction times to ambiguous images predict trial-level intepretations?
```{r reactiontime_behavior,include=FALSE}

# Logistic regression; trial level data.
surprised_trials$positive_response = as.numeric(surprised_trials$P_N_response == "P")
rt_logistic_positiveratings <- glmer(positive_response ~ P_N_response.rt +  (1 | Participant_ID),
                              data = surprised_trials,
                              family = binomial(link="logit"))
summary(rt_logistic_positiveratings)
## Odds ratios and 95% CI.
# Note: This is the same result as the tab_model output.
#library(broom.mixed)
#tidy(rt_logistic_positiveratings,conf.int=TRUE,exponentiate=TRUE,effects="fixed") # Also gives same result.

```

```{r reactiontime_behavior_multilevel_table,echo=FALSE}

# Add transform = NULL if want to see log-odds rather than odds ratio.
tab_model(rt_logistic_positiveratings,
         show.stat = TRUE, show.se = TRUE,
         pred.labels = c("Intercept", "Trial-specific reaction time"),
         dv.labels = c("Likelihood positive rating"),
         string.est = "OR",
         string.se = "standard error",
         string.ci = "95% CI",
         string.stat = "z")

```

# ELA, global functioning, and task behavior.
## ELA and global functioning.
```{r ctq_honos,include=FALSE}
# Association between CTQ and HoNOS scores.
ctq_honos <- lm(HONOS_total_z ~ CTQ_log_z, data = data)
summary(ctq_honos)
confint(ctq_honos,"CTQ_log_z",level = 0.95)
```

```{r ctq_honos_table,echo=FALSE}
#https://strengejacke.github.io/sjPlot/articles/tab_model_estimates.html
tab_model(ctq_honos,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"), # Not sure why but to get DF to show have to use "df.error" here.
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Global functioning impairment (HoNOS z-score)"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error")) # Rename "statistic" in the table to be "t" since it is a t value specifically.
```

## Does ELA relate to negativity biases after controlling for global functioning?
```{r honos_percent_surprised_negative,include=FALSE}
honos_percent_surprised_negative_controlctq <- lm(Percent_Surprised_Negative_Z ~ HONOS_total_z + CTQ_log_z, data = data)
summary(honos_percent_surprised_negative_controlctq)
confint(honos_percent_surprised_negative_controlctq,"CTQ_log_z",level = 0.95)
```

```{r honos_percent_surprised_negative_table,echo=FALSE}
tab_model(honos_percent_surprised_negative_controlctq,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 4, # Lower bound of conidence interval is very small (0.0003) so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),
          pred.labels = c("Intercept", "Global functioning impairment (HoNOS z-score)","ELA (log CTQ score, z-scored)"),
          dv.labels = c("Negativity bias (percent of ambiguous faces interpreted negatively; z-scored)"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

```

## Do ELA and average time spent evaluating ambiguous images (vs. non-ambiguous images) interact to predict global functioning?
```{r ctq_honos_reactiontime,include=FALSE}

# Do CTQ scores and behavioral signatures of ambiguity tolerance (here, time spent evaluating surprised images, 
# regardless of how they categorized them, vs. time spent evaluating angry and happy images) interact to predict HoNOS scores?

# Note: Do not z score these because the unstandardized 0 point is meaningful.
honos_ctq_reactiontime_surprised_vs_angry <- lm(HONOS_total_z ~ CTQ_log_z*rt_difference_surprised_vs_angry, data = data)
summary(honos_ctq_reactiontime_surprised_vs_angry)

simple_slopes(honos_ctq_reactiontime_surprised_vs_angry,
    levels=list(CTQ_log_z=c(-1.5,1.5, 'sstest')))
# For 1.5 (high ELA): beta = 4.36, t = 0.99, p = 0.33.
# For -1.5 (low ELA): beta = -13.28; t = -2.8641; p = 0.007.

honos_ctq_reactiontime_surprised_vs_happy <- lm(HONOS_total_z ~ CTQ_log_z*rt_difference_surprised_vs_happy, data = data)
summary(honos_ctq_reactiontime_surprised_vs_happy)

simple_slopes(honos_ctq_reactiontime_surprised_vs_happy,
    levels=list(CTQ_log_z=c(-1.5,1.5, 'sstest')))
# For 1.5 (high ELA): beta = 7.58, t = 1.38, p = 0.18.
# For -1.5 (low ELA): beta = -13.01; t = -2.78; p = 0.009.

```

```{r ctq_honos_reactiontime_table,echo=FALSE}
# Note: Did not z score difference scores because the unstandardized 0 point is meaningful.
tab_model(honos_ctq_reactiontime_surprised_vs_angry,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),
          pred.labels = c("Intercept",
                          "ELA (log CTQ score, z-scored)",
                          "Average reaction time difference: ambiguous - threatening (s)",
                          "ELA x reaction time difference"),
          dv.labels = c("Global functioning impairment (HoNOS z-score)"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(honos_ctq_reactiontime_surprised_vs_happy,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),
          pred.labels = c("Intercept",
                          "ELA (log CTQ score, z-scored)",
                          "Average reaction time difference:  ambiguous - nonthreatening (s)",
                          "ELA x reaction time difference"),
          dv.labels = c("Global functioning impairment (HoNOS z-score)"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```

# ELA and similarity in representations of ambiguous and threatening stimuli.
```{r ctq_rsa_amygdala,include=FALSE}

## Right amygdala. ##
 
# Angry/surprised.
right_amygdala_log_z_ctq_angrysurprised <- lm(AO_SUR_average_amy_R_Thr50_fisher_z ~ CTQ_log_z, data = data)
summary(right_amygdala_log_z_ctq_angrysurprised)
confint(right_amygdala_log_z_ctq_angrysurprised, 'CTQ_log_z', level=0.95)

# False discovery rate correction.
#p.adjust(anova(right_amygdala_log_z_ctq_angrysurprised)$'Pr(>F)'[1], method = "fdr", n = 8)

# Does effect remain when control for number of voxels?
right_amygdala_log_z_ctq_angrysurprised_controlvoxels <- lm(AO_SUR_average_amy_R_Thr50_fisher_z ~ CTQ_log_z + number_voxels_amy_R_Thr50_average, data = data)
summary(right_amygdala_log_z_ctq_angrysurprised_controlvoxels)
confint(right_amygdala_log_z_ctq_angrysurprised_controlvoxels, 'CTQ_log_z', level=0.95)

# Happy/surprised.
right_amygdala_log_z_ctq_happysurprised <- lm(HO_SUR_average_amy_R_Thr50_fisher_z ~ CTQ_log_z, data = data)
summary(right_amygdala_log_z_ctq_happysurprised)
confint(right_amygdala_log_z_ctq_happysurprised, 'CTQ_log_z', level=0.95)

# Does effect remain after controlling for the number of voxels within the region?
right_amygdala_log_z_ctq_happysurprised_controlvoxels <- lm(HO_SUR_average_amy_R_Thr50_fisher_z ~ CTQ_log_z + number_voxels_amy_R_Thr50_average, data = data)
summary(right_amygdala_log_z_ctq_happysurprised_controlvoxels)
confint(right_amygdala_log_z_ctq_happysurprised_controlvoxels, 'CTQ_log_z', level=0.95)

# Angry/happy.
right_amygdala_log_z_ctq_angryhappy <- lm(AO_HO_average_amy_R_Thr50_fisher_z ~ CTQ_log_z, data = data)
summary(right_amygdala_log_z_ctq_angryhappy)
confint(right_amygdala_log_z_ctq_angryhappy, 'CTQ_log_z', level=0.95)

## Left amygdala. ##

# Angry/Surprised.
left_amygdala_log_z_ctq_angrysurprised <- lm(AO_SUR_average_amy_L_Thr50_fisher_z ~ CTQ_log_z, data = data)
summary(left_amygdala_log_z_ctq_angrysurprised)
confint(left_amygdala_log_z_ctq_angrysurprised, 'CTQ_log_z', level=0.95)

# Does effect remain after controlling for the number of voxels within the region?
left_amygdala_log_z_ctq_angrysurprised_controlvoxels <- lm(AO_SUR_average_amy_L_Thr50_fisher_z  ~ CTQ_log_z + number_voxels_amy_L_Thr50_average, data = data)
summary(left_amygdala_log_z_ctq_angrysurprised_controlvoxels)
confint(left_amygdala_log_z_ctq_angrysurprised_controlvoxels, 'CTQ_log_z', level=0.95)

# Happy/surprised.
left_amygdala_log_z_ctq_happysurprised<- lm(HO_SUR_average_amy_L_Thr50_fisher_z  ~ CTQ_log_z, data = data)
summary(left_amygdala_log_z_ctq_happysurprised)
confint(left_amygdala_log_z_ctq_happysurprised, 'CTQ_log_z', level=0.95)

# Angry/happy.
left_amygdala_log_z_ctq_angryhappy <- lm(AO_HO_average_amy_L_Thr50_fisher_z  ~ CTQ_log_z, data = data)
summary(left_amygdala_log_z_ctq_angryhappy)
confint(left_amygdala_log_z_ctq_angryhappy, 'CTQ_log_z', level=0.95)
```

```{r ctq_rsa_accumbens,include=FALSE}

## Right accumbens. ##
# Angry/surprised.
right_accumbens_log_z_ctq_angrysurprised <- lm(AO_SUR_average_accumbens_R_Thr25_fisher_z ~ CTQ_log_z, data = data)
summary(right_accumbens_log_z_ctq_angrysurprised)
confint(right_accumbens_log_z_ctq_angrysurprised,"CTQ_log_z",level = 0.95)

# Does effect remain after controlling for the number of voxels within the region?
right_accumbens_log_z_ctq_angrysurprised_controlvoxels <- lm(AO_SUR_average_accumbens_R_Thr25_fisher_z  ~ CTQ_log_z + number_voxels_accumbens_R_Thr25_average, data = data)
summary(right_accumbens_log_z_ctq_angrysurprised_controlvoxels)
confint(right_accumbens_log_z_ctq_angrysurprised_controlvoxels,"CTQ_log_z",level = 0.95)

# Happy/surprised.
right_accumbens_log_z_ctq_happysurprised <- lm(HO_SUR_average_accumbens_R_Thr25_fisher_z ~ CTQ_log_z, data = data)
summary(right_accumbens_log_z_ctq_happysurprised)
confint(right_accumbens_log_z_ctq_happysurprised,"CTQ_log_z",level = 0.95)

# Angry/happy.
right_accumbens_log_z_ctq_angryhappy <- lm(AO_HO_average_accumbens_R_Thr25_fisher_z ~ CTQ_log_z, data = data)
summary(right_accumbens_log_z_ctq_angryhappy)
confint(right_accumbens_log_z_ctq_angryhappy,"CTQ_log_z",level = 0.95)

## Left accumbens. ##

# Angry/surprised.
left_accumbens_log_z_ctq_angrysurprised <- lm(AO_SUR_average_accumbens_L_Thr25_fisher_z ~ CTQ_log_z, data = data)
summary(left_accumbens_log_z_ctq_angrysurprised)
confint(left_accumbens_log_z_ctq_angrysurprised,"CTQ_log_z",level=0.95)

# Does effect remain after controlling for the number of voxels within the region?
left_accumbens_log_z_ctq_angrysurprised_controlvoxels <- lm(AO_SUR_average_accumbens_L_Thr25_fisher_z  ~ CTQ_log_z + number_voxels_accumbens_L_Thr25_average, data = data)
summary(left_accumbens_log_z_ctq_angrysurprised_controlvoxels)
confint(left_accumbens_log_z_ctq_angrysurprised_controlvoxels,"CTQ_log_z",level = 0.95)

# Happy/surprised.
left_accumbens_log_z_ctq_happysurprised <- lm(HO_SUR_average_accumbens_L_Thr25_fisher_z ~ CTQ_log_z, data = data)
summary(left_accumbens_log_z_ctq_happysurprised)
confint(left_accumbens_log_z_ctq_happysurprised,"CTQ_log_z",level = 0.95)

# Angry/happy.
left_accumbens_log_z_ctq_angryhappy <- lm(AO_HO_average_accumbens_L_Thr25_fisher_z ~ CTQ_log_z, data = data)
summary(left_accumbens_log_z_ctq_angryhappy)
confint(left_accumbens_log_z_ctq_angryhappy,"CTQ_log_z",level = 0.95)

```

```{r ctq_rsa_anteriorinsula,include=FALSE}

## Right anterior insula. ##

# Angry/surprised.
right_anteriorinsula_log_z_ctq_angrysurprised <- lm(AO_SUR_average_anteriorinsula_R_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(right_anteriorinsula_log_z_ctq_angrysurprised)
confint(right_anteriorinsula_log_z_ctq_angrysurprised,"CTQ_log_z",level=0.95)

# Does effect remain after controlling for the number of voxels within the region?
right_anteriorinsula_log_z_ctq_angrysurprised_controlvoxels <- lm(AO_SUR_average_anteriorinsula_R_xu2021_fisher_z  ~ CTQ_log_z + number_voxels_anteriorinsula_R_xu2021_average, data = data)
summary(right_anteriorinsula_log_z_ctq_angrysurprised_controlvoxels)
confint(right_anteriorinsula_log_z_ctq_angrysurprised_controlvoxels,"CTQ_log_z",level=0.95)

# Happy/surprised.
right_anteriorinsula_log_z_ctq_happysurprised <- lm(HO_SUR_average_anteriorinsula_R_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(right_anteriorinsula_log_z_ctq_happysurprised)
confint(right_anteriorinsula_log_z_ctq_happysurprised,"CTQ_log_z",level=0.95)

# Angry/happy.
right_anteriorinsula_log_z_ctq_angryhappy <- lm(AO_HO_average_anteriorinsula_R_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(right_anteriorinsula_log_z_ctq_angryhappy)
confint(right_anteriorinsula_log_z_ctq_angryhappy,"CTQ_log_z",level=0.95)

# Does effect remain after controlling for the number of voxels within the region?
right_anteriorinsula_log_z_ctq_angryhappy_controlvoxels <- lm(AO_HO_average_anteriorinsula_R_xu2021_fisher_z  ~ CTQ_log_z + number_voxels_anteriorinsula_R_xu2021_average, data = data)
summary(right_anteriorinsula_log_z_ctq_angryhappy_controlvoxels)
confint(right_anteriorinsula_log_z_ctq_angryhappy_controlvoxels,"CTQ_log_z",level=0.95)

## Left anterior insula. ##

# Angry/surprised.
left_anteriorinsula_log_z_ctq_angrysurprised <- lm(AO_SUR_average_anteriorinsula_L_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(left_anteriorinsula_log_z_ctq_angrysurprised)
confint(left_anteriorinsula_log_z_ctq_angrysurprised,"CTQ_log_z",level=0.95)

# Does effect remain after controlling for the number of voxels within the region?
left_anteriorinsula_log_z_ctq_angrysurprised_controlvoxels <- lm(AO_SUR_average_anteriorinsula_L_xu2021_fisher_z  ~ CTQ_log_z + number_voxels_anteriorinsula_L_xu2021_average, data = data)
summary(left_anteriorinsula_log_z_ctq_angrysurprised_controlvoxels)
confint(left_anteriorinsula_log_z_ctq_angrysurprised_controlvoxels,"CTQ_log_z",level=0.95)

# Happy/surprised.
left_anteriorinsula_log_z_ctq_happysurprised <- lm(HO_SUR_average_anteriorinsula_L_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(left_anteriorinsula_log_z_ctq_happysurprised)
confint(left_anteriorinsula_log_z_ctq_happysurprised,"CTQ_log_z",level=0.95)

# Angry/happy.
left_anteriorinsula_log_z_ctq_angryhappy <- lm(AO_HO_average_anteriorinsula_L_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(left_anteriorinsula_log_z_ctq_angryhappy)
confint(left_anteriorinsula_log_z_ctq_angryhappy,"CTQ_log_z",level=0.95)
```

```{r ctq_rsa_vmpfc,include=FALSE}

## Right vmPFC. ##

# Angry/surprised.
right_vmpfc_log_z_ctq_angrysurprised <- lm(AO_SUR_average_vmpfc_R_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(right_vmpfc_log_z_ctq_angrysurprised)
confint(right_vmpfc_log_z_ctq_angrysurprised,"CTQ_log_z",level=0.95)

# Does effect remain after controlling for the number of voxels within the region?
right_vmpfc_log_z_ctq_angrysurprised_controlvoxels <- lm(AO_SUR_average_vmpfc_R_xu2021_fisher_z  ~ CTQ_log_z + number_voxels_vmpfc_R_xu2021_average, data = data)
summary(right_vmpfc_log_z_ctq_angrysurprised_controlvoxels)
confint(right_vmpfc_log_z_ctq_angrysurprised_controlvoxels,"CTQ_log_z",level=0.95)

# Happy/surprised.
right_vmpfc_log_z_ctq_happysurprised <- lm(HO_SUR_average_vmpfc_R_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(right_vmpfc_log_z_ctq_happysurprised)
confint(right_vmpfc_log_z_ctq_happysurprised,"CTQ_log_z",level=0.95)

# Angry/happy.
right_vmpfc_log_z_ctq_angryhappy <- lm(AO_HO_average_vmpfc_R_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(right_vmpfc_log_z_ctq_angryhappy)
confint(right_vmpfc_log_z_ctq_angryhappy,"CTQ_log_z",level=0.95)

## Left vmPFC. ##

# Angry/surprised.
left_vmpfc_log_z_ctq_angrysurprised <- lm(AO_SUR_average_vmpfc_L_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(left_vmpfc_log_z_ctq_angrysurprised)
confint(left_vmpfc_log_z_ctq_angrysurprised,"CTQ_log_z",level=0.95)

# Does effect remain after controlling for the number of voxels within the region?
left_vmpfc_log_z_ctq_angrysurprised_controlvoxels <- lm(AO_SUR_average_vmpfc_L_xu2021_fisher_z  ~ CTQ_log_z + number_voxels_vmpfc_L_xu2021_average, data = data)
summary(left_vmpfc_log_z_ctq_angrysurprised_controlvoxels)
confint(left_vmpfc_log_z_ctq_angrysurprised_controlvoxels,"CTQ_log_z",level=0.95)

# Happy/surprised.
left_vmpfc_log_z_ctq_happysurprised <- lm(HO_SUR_average_vmpfc_L_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(left_vmpfc_log_z_ctq_happysurprised)
confint(left_vmpfc_log_z_ctq_happysurprised,"CTQ_log_z",level=0.95)

# Angry/happy.
left_vmpfc_log_z_ctq_angryhappy <- lm(AO_HO_average_vmpfc_L_xu2021_fisher_z ~ CTQ_log_z, data = data)
summary(left_vmpfc_log_z_ctq_angryhappy)
confint(left_vmpfc_log_z_ctq_angryhappy,"CTQ_log_z",level=0.95)
```

```{r ctq_rsa_v1,include=FALSE}

## Right V1. ##

# Angry/surprised.
right_V1_log_z_ctq_angrysurprised <- lm(AO_SUR_average_V1_R_Thr75_fisher_z ~ CTQ_log_z, data = data)
summary(right_V1_log_z_ctq_angrysurprised)
confint(right_V1_log_z_ctq_angrysurprised,"CTQ_log_z",level=0.95)

# Control voxels; just for consistency with other models and for the table.
right_V1_log_z_ctq_angrysurprised_controlvoxels <- lm(AO_SUR_average_V1_R_Thr75_fisher_z  ~ CTQ_log_z + number_voxels_V1_R_Thr75_average, data = data)
summary(right_V1_log_z_ctq_angrysurprised_controlvoxels)
confint(right_V1_log_z_ctq_angrysurprised_controlvoxels,"CTQ_log_z",level=0.95)

# Happy/surprised.
right_V1_log_z_ctq_happysurprised <- lm(HO_SUR_average_V1_R_Thr75_fisher_z ~ CTQ_log_z, data = data)
summary(right_V1_log_z_ctq_happysurprised)
confint(right_V1_log_z_ctq_happysurprised,"CTQ_log_z",level=0.95)
# not significant.

# Angry/happy.
right_V1_log_z_ctq_angryhappy <- lm(AO_HO_average_V1_R_Thr75_fisher_z ~ CTQ_log_z, data = data)
summary(right_V1_log_z_ctq_angryhappy)
confint(right_V1_log_z_ctq_angryhappy,"CTQ_log_z",level=0.95)

## Left V1. ##

# Angry/surprised.
left_V1_log_z_ctq_angrysurprised <- lm(AO_SUR_average_V1_L_Thr75_fisher_z ~ CTQ_log_z, data = data)
summary(left_V1_log_z_ctq_angrysurprised)
confint(left_V1_log_z_ctq_angrysurprised,"CTQ_log_z",level=0.95)

# Control voxels; just for consistency with other models and for the table.
left_V1_log_z_ctq_angrysurprised_controlvoxels <- lm(AO_SUR_average_V1_L_Thr75_fisher_z  ~ CTQ_log_z + number_voxels_V1_L_Thr75_average, data = data)
summary(left_V1_log_z_ctq_angrysurprised_controlvoxels)
confint(left_V1_log_z_ctq_angrysurprised_controlvoxels,"CTQ_log_z",level=0.95)

# Happy/surprised.
left_V1_log_z_ctq_happysurprised <- lm(HO_SUR_average_V1_L_Thr75_fisher_z ~ CTQ_log_z, data = data)
summary(left_V1_log_z_ctq_happysurprised)

# Angry/happy.
left_V1_log_z_ctq_angryhappy <- lm(AO_HO_average_V1_L_Thr75_fisher_z ~ CTQ_log_z, data = data)
summary(left_V1_log_z_ctq_angryhappy)
confint(left_V1_log_z_ctq_angryhappy,"CTQ_log_z",level=0.95)
```

```{r ctq_rsa_table_ambiguousthreatening_amygdala,echo=FALSE}

tab_model(right_amygdala_log_z_ctq_angrysurprised,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Right amygdala"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(left_amygdala_log_z_ctq_angrysurprised,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Left amygdala"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```

```{r ctq_rsa_table_ambiguousthreatening_accumbens,echo=FALSE}

tab_model(right_accumbens_log_z_ctq_angrysurprised,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Right nucleus accumbens"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(left_accumbens_log_z_ctq_angrysurprised,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Left nucleus accumbens"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```

```{r ctq_rsa_table_ambiguousthreatening_anteriorinsula,echo=FALSE}

tab_model(right_anteriorinsula_log_z_ctq_angrysurprised,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Right anterior insula"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(left_anteriorinsula_log_z_ctq_angrysurprised,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 3, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Left anterior insula"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```

```{r ctq_rsa_table_ambiguousthreatening_vmpfc,echo=FALSE}

tab_model(right_vmpfc_log_z_ctq_angrysurprised,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Right vmPFC"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(left_vmpfc_log_z_ctq_angrysurprised,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 3, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Left vmPFC"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```

```{r ctq_rsa_table_ambiguousthreatening_V1,echo=FALSE}

tab_model(right_V1_log_z_ctq_angrysurprised,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Right V1"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(left_V1_log_z_ctq_angrysurprised,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 3, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Left V1"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```

```{r calculate_corrected_pvalues,include=FALSE}
# Get model information.
right_amygdala <- as.data.frame(coef(summary(right_amygdala_log_z_ctq_angrysurprised)))
right_amygdala$variable <- row.names(right_amygdala)
rownames(right_amygdala) <- NULL
right_amygdala$region <- "right amygdala"

left_amygdala <- as.data.frame(coef(summary(left_amygdala_log_z_ctq_angrysurprised)))
left_amygdala$variable <- row.names(left_amygdala)
rownames(left_amygdala) <- NULL
left_amygdala$region <- "left amygdala"

right_accumbens <- as.data.frame(coef(summary(right_accumbens_log_z_ctq_angrysurprised)))
right_accumbens$variable <- row.names(right_accumbens)
rownames(right_accumbens) <- NULL
right_accumbens$region <- "right nucleus accumbens"

left_accumbens <- as.data.frame(coef(summary(left_accumbens_log_z_ctq_angrysurprised)))
left_accumbens$variable <- row.names(left_accumbens)
rownames(left_accumbens) <- NULL
left_accumbens$region <- "left nucleus accumbens"

right_anteriorinsula <- as.data.frame(coef(summary(right_anteriorinsula_log_z_ctq_angrysurprised)))
right_anteriorinsula$variable <- row.names(right_anteriorinsula)
rownames(right_anteriorinsula) <- NULL
right_anteriorinsula$region <- "right anterior insula"

left_anteriorinsula <- as.data.frame(coef(summary(left_anteriorinsula_log_z_ctq_angrysurprised)))
left_anteriorinsula$variable <- row.names(left_anteriorinsula)
rownames(left_anteriorinsula) <- NULL
left_anteriorinsula$region <- "left anterior insula"

right_vmpfc <- as.data.frame(coef(summary(right_vmpfc_log_z_ctq_angrysurprised)))
right_vmpfc$variable <- row.names(right_vmpfc)
rownames(right_vmpfc) <- NULL
right_vmpfc$region <- "right vmPFC"

left_vmpfc <- as.data.frame(coef(summary(left_vmpfc_log_z_ctq_angrysurprised)))
left_vmpfc$variable <- row.names(left_vmpfc)
rownames(left_vmpfc) <- NULL
left_vmpfc$region <- "left vmPFC"

right_V1 <- as.data.frame(coef(summary(right_V1_log_z_ctq_angrysurprised)))
right_V1$variable <- row.names(right_V1)
rownames(right_V1) <- NULL
right_V1$region <- "right V1"

left_V1 <- as.data.frame(coef(summary(left_V1_log_z_ctq_angrysurprised)))
left_V1$variable <- row.names(left_V1)
rownames(left_V1) <- NULL
left_V1$region <- "left V1"

model_information <- bind_rows(right_amygdala,left_amygdala,
                               right_accumbens,left_accumbens,
                               right_anteriorinsula, left_anteriorinsula,
                               right_vmpfc, left_vmpfc,
                               right_V1, left_V1)

model_information$estimate <- model_information$Estimate
model_information$Estimate <- NULL
model_information$p.value <- model_information$`Pr(>|t|)`
model_information$`Pr(>|t|)` <- NULL
model_information$t.value <-model_information$`t value`
model_information <- subset(model_information,variable == "CTQ_log_z")

model_information <- model_information %>% select(region,estimate, t.value, p.value)

model_information$q.value <- stats::p.adjust(model_information$p, method = 'fdr', n = nrow(model_information))


```

```{r ctq_rsa_qvalues_table,echo=FALSE}
knitr::kable(model_information, 
             row.names = FALSE,
             col.names =  c("Region","Standardized beta estimate", "t value", "uncorrected p value", "FDR corrected q value"),
                     caption = "False discovery rate corrected q-values",
        escape = FALSE,
        format="html",
        align = "l",
        digits = 3,
        booktabs = TRUE,
        longtable = TRUE,
        linesep = "")  %>%
        row_spec(0,bold=TRUE) %>% 
        kableExtra::kable_styling(
        position = "left",
        latex_options = c("striped", "repeat_header"),
        stripe_color = "gray!15") %>%
  kable_styling(position = "left")
      
```

## Do observed associations with ambiguous/threatening overlap hold when we control for participant-specific ROI size?
```{r ctq_rsa_controlvoxels_table_ambiguousthreatening_amygdala,echo=FALSE}

tab_model(right_amygdala_log_z_ctq_angrysurprised_controlvoxels,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 5, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)", "Right amygdala size"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Right amygdala"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(left_amygdala_log_z_ctq_angrysurprised_controlvoxels,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 4, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)", "Left amygdala size"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Left amygdala"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```

```{r ctq_rsa_controlvoxels_table_ambiguousthreatening_accumbens,echo=FALSE}

tab_model(right_accumbens_log_z_ctq_angrysurprised_controlvoxels,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 4, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)", "Right nucleus accumbens size"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Right nucleus accumbens"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(left_accumbens_log_z_ctq_angrysurprised_controlvoxels,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 4, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)", "Left nucleus accumbens size"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Left nucleus accumbens"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```

```{r ctq_rsa_controlvoxels_table_ambiguousthreatening_anteriorinsula,echo=FALSE}
tab_model(right_anteriorinsula_log_z_ctq_angrysurprised_controlvoxels,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 4, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)", "Right anterior insula size"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Right anterior insula"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(left_anteriorinsula_log_z_ctq_angrysurprised_controlvoxels,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 4, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)", "Left anterior insula size"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Left anterior insula"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```

```{r ctq_rsa_controlvoxels_table_ambiguousthreatening_vmpfc,echo=FALSE}
tab_model(right_vmpfc_log_z_ctq_angrysurprised_controlvoxels,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 4, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)", "Right vmPFC size"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Right vmPFC"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(left_vmpfc_log_z_ctq_angrysurprised_controlvoxels,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 4, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)", "Left vmPFC size"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Left vmPFC"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```

```{r ctq_rsa_controlvoxels_table_ambiguousthreatening_V1,echo=FALSE}
tab_model(right_V1_log_z_ctq_angrysurprised_controlvoxels,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 4, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)", "Right V1 size"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Right V1"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))

tab_model(left_V1_log_z_ctq_angrysurprised_controlvoxels,
          show.stat = TRUE, show.df = TRUE, show.se = TRUE,
          digits = 4, # It is very small so was saying zero when using default of two decimal points.
          col.order = c( "est", "ci", "stat", "df.error", "se", "p"),  
          pred.labels = c("Intercept", "ELA (log CTQ score, z-scored)", "Left V1 size"),
          dv.labels = c("Ambiguous/threatening overlap (Fisher z score): Left V1"),
          strings = c(est = "beta coefficient", ci ="95% CI", stat = "t", df = "DF", se = "standard error"))
```
